---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Overview

The goal of hw3forBios625 is to develop an R package implementing an existing R function.

# linearRegression

<!-- badges: start -->
[![R-CMD-check](https://github.com/haoyi1102/hw3forBios625/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/haoyi1102/hw3forBios625/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/haoyi1102/hw3forBios625/branch/master/graph/badge.svg)](https://app.codecov.io/gh/haoyi1102/hw3forBios625?branch=master)
<!-- badges: end -->

The goal of linearRegression is to performing linear regression analysis. This package allows users to easily compute linear regression coefficients, residuals, standard errors, t-values, p-values, multiple R-squared, F-statistic, and p-value for the F-statistic for any given dataset.


## Installation

You can install the development version of linearRegression from [GitHub](https://github.com/) with:

```{r}
#install.packages("devtools") --> 
devtools::install_github("haoyi1102/hw3forBios625")
```
## dataset
```{r}
# Load the package
library(linearRegression)

#load example dataset
data("testdata")
names(data)
```
Check out the help page for the `testdata` data set using `?testdata`

## Usage
After installation, load the package and use the 'linearRegression' function as follows:

```{r}
library(linearRegression)

# Basic usage
#result <- linearRegression(outcome_name = "OutcomeVariable", 
#                           predictor_name = "PredictorVariable", 
#                           data = YourDataFrame, 
#                           plot = TRUE)
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Load the package
library(linearRegression)

#Perform linear regression
result <- linearRegression("Optimism", "Age", data = data , plot = TRUE)

#view the results
print(result)
```

## Getting Help

If you encounter any issues or have questions about the 'linearRegression' package:

1. Refer to the in-built documentation by calling '?linearRegression' in R.

2. Check the vignettes for detailed examples and use cases.
