---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linearRegression

<!-- badges: start -->
[![R-CMD-check](https://github.com/haoyi1102/hw3forBios625/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/haoyi1102/hw3forBios625/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/haoyi1102/hw3forBios625/branch/master/graph/badge.svg)](https://app.codecov.io/gh/haoyi1102/hw3forBios625?branch=master)
<!-- badges: end -->

The goal of linearRegression is to performing linear regression analysis. This package allows users to easily compute linear regression coefficients, residuals, standard errors, t-values, p-values, multiple R-squared, F-statistic, and p-value for the F-statistic for any given dataset.


## Installation

You can install the development version of linearRegression from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("haoyi1102/hw3forBios625")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Load the package
library(linearRegression)

#load example dataset
data <- data.frame(
  Outcome = c(1, 2, 3, 4, 5),
  Predictor = c(2, 3, 4, 5, 6)
)

#Perform linear regression
result <- linearRegression("Outcome", "Predictor", data)

#view the results
print(result)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

