---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Overview

The goal of hw3forBios625 is to develop an R package implementing an existing R function.

# linearRegression

<!-- badges: start -->
[![R-CMD-check](https://github.com/haoyi1102/hw3forBios625/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/haoyi1102/hw3forBios625/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/haoyi1102/hw3forBios625/branch/master/graph/badge.svg)](https://app.codecov.io/gh/haoyi1102/hw3forBios625?branch=master)
<!-- badges: end -->

The goal of linearRegression is to performing linear regression analysis. This package allows users to easily compute linear regression coefficients, residuals, standard errors, t-values, p-values, multiple R-squared, F-statistic, and p-value for the F-statistic for any given dataset.


## Installation

You can install the development version of linearRegression from [GitHub](https://github.com/) with:

```{r}
#install.packages("devtools") --> 
devtools::install_github("haoyi1102/hw3forBios625")
```
## dataset
```{r}
# Load the package
library(linearRegression)

#load example dataset
data("testdata")
names(data)
```
Check out the help page for the `data` data set using `?data`

## Usage
After installation, load the package and use the 'linearRegression' function as follows:

```{r}
library(linearRegression)

# Basic usage
#result <- linearRegression(outcome_name = "OutcomeVariable", 
#                           predictor_name = "PredictorVariable", 
#                           data = YourDataFrame, 
#                           plot = TRUE)
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Load the package
library(linearRegression)

#Perform linear regression
result <- linearRegression("Optimism", "Age", data = data , plot = TRUE)

#view the results
print(result)
```


## Test correctness and efficiency
The comparison(s) against the original R function(s) on simulated or real datasets clearly and sufficiently demonstrate both correctness and efficiency of the function(s) implemented in the R package.

```{r}
library(linearRegression)

# Load test data
data("testdata")

# Run the custom linear regression function
m <- linearRegression("Optimism", "Age", data)

# Run the built-in lm() function and summarize it
m1 <- summary(lm(Optimism ~ Age, data))
```

Test correctness
```{r}
library(testthat)

test_that("linearRegression matches lm function results", {
  
  # Compare Residuals
 
  expect_equal(m$Residuals, as.vector(fivenum(m1$residuals)))

  # Compare Coefficients
  # Extract coefficients from the custom model
  custom_coeffs <- m$Coefficients$Estimate

  # Extract coefficients from the lm model summary
  lm_coeffs <- m1$coefficients[, "Estimate"]

  # Expect the coefficients from the custom model to match those from the lm model
  expect_equal(custom_coeffs, as.vector(lm_coeffs))

  # Compare Multiple R-squared
  # Expect the Multiple R-squared from the custom model to match that from the lm model
  expect_equal(m$`Multiple R-squared`, m1$r.squared)

  # Compare F-statistic
  # Expect the F-statistic from the custom model to match that from the lm model
  expect_equal(m$`F-statistic`, as.vector(m1$fstatistic[1]))

  # Compare p-value of F-statistic
  # Calculate p-value for F-statistic from the lm model
  p_value_f_lm <-
    pf(m1$fstatistic[1], m1$fstatistic[2], m1$fstatistic[3], lower.tail = FALSE)

  # Expect the p-value from the custom model to match the calculated p-value from the lm model.
  expect_equal(m$`p-value`, as.vector(p_value_f_lm))

})


```

Test efficiency
```{r setup}

# bench::mark for estimate
bench::mark(
  m$Coefficients$Estimate, 
  as.vector(m1$coefficients[, "Estimate"]),
  iterations = 10,
  check = TRUE
)

# bench::mark for F- statistic
bench::mark(
  m$`F-statistic`, 
  as.vector(m1$fstatistic[1]),
  iterations = 10,
  check = TRUE
)

# bench::mark for p-value

p_value_f_lm <-
    pf(m1$fstatistic[1], m1$fstatistic[2], m1$fstatistic[3], lower.tail = FALSE)

bench::mark(
  m$`p-value`, 
  as.vector(p_value_f_lm),
  iterations = 10,
  check = TRUE
)

```

## Getting Help

If you encounter any issues or have questions about the 'linearRegression' package:

1. Refer to the in-built documentation by calling '?linearRegression' in R.

2. Check the vignettes for detailed examples and use cases.
