---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette demonstrates the use of the `linearRegression` function from the [YourPackageName] package. The `linearRegression` function is designed to perform linear regression analysis and provide diagnostic plots for model assessment. 

# Installation

You can install the [linearRegression] from github:

```{r}
#install.packages("devtools") --> 
#devtools::install_github("haoyi1102/hw3forBios625")
```

# Example Usage

## Loading the Package
```{r}
library(linearRegression)
```

## dataset
```{r}
# Load the package
library(linearRegression)

#load example dataset
data("testdata")
names(data)
```
Check out the help page for the `testdata` data set using `?testdata`

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Load the package
library(linearRegression)

#Perform linear regression
result <- linearRegression("Optimism", "Age", data = data , plot = TRUE)

#view the results
print(result)
```
`

## Test correctness and efficiency
The comparison(s) against the original R function(s) on simulated or real datasets clearly and sufficiently demonstrate both correctness and efficiency of the function(s) implemented in the R package.

```{r}
library(linearRegression)

# Load test data
data("testdata")

# Run the custom linear regression function
m <- linearRegression("Optimism", "Age", data)

# Run the built-in lm() function and summarize it
m1 <- summary(lm(Optimism ~ Age, data))
```

Test correctness
```{r}
library(testthat)

test_that("linearRegression matches lm function results", {
  
  # Compare Residuals
 
  expect_equal(m$Residuals, as.vector(fivenum(m1$residuals)))

  # Compare Coefficients
  # Extract coefficients from the custom model
  custom_coeffs <- m$Coefficients$Estimate

  # Extract coefficients from the lm model summary
  lm_coeffs <- m1$coefficients[, "Estimate"]

  # Expect the coefficients from the custom model to match those from the lm model
  expect_equal(custom_coeffs, as.vector(lm_coeffs))

  # Compare Multiple R-squared
  # Expect the Multiple R-squared from the custom model to match that from the lm model
  expect_equal(m$`Multiple R-squared`, m1$r.squared)

  # Compare F-statistic
  # Expect the F-statistic from the custom model to match that from the lm model
  expect_equal(m$`F-statistic`, as.vector(m1$fstatistic[1]))

  # Compare p-value of F-statistic
  # Calculate p-value for F-statistic from the lm model
  p_value_f_lm <-
    pf(m1$fstatistic[1], m1$fstatistic[2], m1$fstatistic[3], lower.tail = FALSE)

  # Expect the p-value from the custom model to match the calculated p-value from the lm model .
  expect_equal(m$`p-value`, as.vector(p_value_f_lm))

})


```

Test efficiency
```{r setup}

# Extract coefficients from the custom model
  custom_coeffs <- m$Coefficients$Estimate

# Extract coefficients from the lm model summary
  lm_coeffs <- m1$coefficients[, "Estimate"]

```

